% FortySecondsCV LaTeX template
% Copyright © 2019-2020 René Wirnata <rene.wirnata@pandascience.net>
% Licensed under the 3-Clause BSD License. See LICENSE file for details.
% Please visit https://github.com/PandaScience/FortySecondsCV for the most
% recent version! For bugs or feature requests, please open a new issue on
% github.
%
% Contributors
% ------------
% * ifokkema
% * Bertbk
% * Hespe
%
% Attributions
% ------------
% * fortysecondscv is based on the twentysecondcv class by Carmine Spagnuolo
%   (cspagnuolo@unisa.it), released under the MIT license and available under
%   https://github.com/spagnuolocarmine/TwentySecondsCurriculumVitae-LaTex
% * further attributions are indicated immediately before corresponding code


%-------------------------------------------------------------------------------
%                             ADDITIONAL PACKAGES
%-------------------------------------------------------------------------------
\documentclass[
	a4paper,
	 maincolor=cvgreen,
	 sectioncolor=cvgreen,
	 subsectioncolor=cvgreen,
	 itemtextcolor=antracite!80,
	 profilepicstyle=profilecircle,
]{fortysecondscv}

% improve word spacing and hyphenation
\usepackage{microtype}
\usepackage{ragged2e}

% uncomment in case you don't want any hyphenation
\usepackage[none]{hyphenat}

% take care of proper font encoding
\ifxetexorluatex
	\usepackage{fontspec}
	\defaultfontfeatures{Ligatures=TeX}
\else
	\usepackage[utf8]{inputenc}
	\usepackage[T1]{fontenc}
\fi

% enable mathematical syntax for some symbols like \varnothing
\usepackage{amssymb}
\newcommand{\slightlylarger}{\fontsize{11pt}{12pt}\selectfont}

% bubble diagram configuration
\usepackage{smartdiagram}
\smartdiagramset{
	% default font size is \large, so adjust to harmonize with sidebar layout
	bubble center node font = \footnotesize,
	bubble node font = \footnotesize,
	% default: 4cm/2.5cm; make minimum diameter relative to sidebar size
	bubble center node size = 0.4\sidebartextwidth,
	bubble node size = 0.25\sidebartextwidth,
	distance center/other bubbles = 1.5em,
	% set center bubble color
	bubble center node color = maincolor!70,
	% define the list of colors usable in the diagram
	set color list = {maincolor!10, maincolor!40,
	maincolor!20, maincolor!60, maincolor!35},
	% sets the opacity at which the bubbles are shown
	bubble fill opacity = 0.8,
}


%-------------------------------------------------------------------------------
%                            PERSONAL INFORMATION
%-------------------------------------------------------------------------------
%% mandatory information
% your name
\cvname{\begin{center} \textbf{\\[20pt] Riccardo Barbieri}\end {center}}
% job title/career
\cvjobtitle{\begin{center}\textbf{\LARGE AI Engineer}\end {center}}

%% optional information
% profile picture
%\cvprofilepic{pics/self.png}

% NOTE: ordering in sidebar will mimic the following order
\cvphone{+00 0000000000}
% personal website
%\cvsite{https://pandascience.net}
% email address
\cvaddress{email@email.com}
\cvLinkedin{rbarb}
\cvgithub{RiccardoBarb}


%-------------------------------------------------------------------------------
%                              SIDEBAR 1st PAGE
%-------------------------------------------------------------------------------
% add more profile sections to sidebar on first page
\addtofrontsidebar{
	% include gosquare national flags from https://github.com/gosquared/flags;
	% naming according to ISO 3166-1 alpha-2 country codes
	\graphicspath{{pics/flags/}}


	\profilesection{Technical Skills}
	\begin{sidebarminipage}
        \fontsize{9.5pt}{11pt}\selectfont
		\chartlabel{ML}
		\chartlabel{NLP}
		\chartlabel{MLOps}
		\chartlabel{Deep Learning}
		\chartlabel{Data Pipelines}
		\chartlabel{LLM Workflows}
		\chartlabel{RAG}
		\chartlabel{Experimentation}
		\chartlabel{Evaluation}

	\end{sidebarminipage}

    \skill{}{\textbf{Programming:} \emph{Python, SQL, MATLAB, R}}
    \skill{}{\textbf{ML \& DL:} \emph{Scikit-learn, PyTorch, spaCy, Transformers}}
    \skill{}{\textbf{LLM \& RAG:} \emph{LangChain, LangGraph, Pocketflow, Vector DBs}}
    \skill{}{\textbf{Data Pipelines:} \emph{Pandas, NumPy, Spark, Databricks}}
    \skill{}{\textbf{Cloud \& DevOps:} \emph{AWS, Azure, Docker, Git}}


\profilesection{Transferable Skills}

		\skill{}{\textbf{Project Management:}\emph{\slightlylarger{\\{I manage complex projects involving ML, statistical modeling and AI. I collaborate with multidisciplinary teams, adapting to changing contexts to achieve ambitious goals, even with limited resources.}}}}
		\skill{}{\textbf{Creative Thinking and Problem Solving:}\emph{\slightlylarger{\\{I develop innovative solutions for LLM-based systems such as RAG and agents, ML applications, predictive models and data pipelines. I combine an analytical approach with an experimental mindset, with a strong focus on scalability and generalizability.}}}}
		\skill{}{\textbf{Interpersonal Skills:}\emph{\slightlylarger{\\{I collaborate effectively with research, data \& analytics, data science, and AI engineering teams. I support junior colleagues and facilitate knowledge transfer. I am regarded as a positive and optimistic team member who helps build constructive working relationships.}}}}

}

%-------------------------------------------------------------------------------
%                         TABLE ENTRIES RIGHT COLUMN
%-------------------------------------------------------------------------------
\begin{document}

\makefrontsidebar

\cvsection{\huge {Work Experience}}
\begin{cvtable}[2]
    \cvitem{\textbf{\Large{\href{https://www.bitbang.com}{BitBang}}}\hspace{0.5em}\slightlylarger{(2021 - Ongoing)}\hspace{0.5em}}{\slightlylarger{Bologna}}{}{}
    \cvitem{\Large{AI Engineer}\hspace{0.5em}\slightlylarger{(2024 - Ongoing)}}{}
    {\\[-0.5em]\slightlylarger{\emph{Development, design, and deployment of systems based on LLM and ML.}}
    \addtolength{\leftmargini}{-1.3em}
    \begin{itemize}
        \setlength\itemsep{-0.1em}
        \setlength\topsep{-0.1em}
        \item \textbf{Enterprise LLM workflows:} Technical lead in the development of LLM-based systems (RAG and agents). Designed and implemented ingestion and retrieval pipelines for multiple products across different business units. Coordinated a cross-functional team to support the progressive evolution of the system into an enterprise AI platform.
        \item \textbf{Automation \& classification:} Responsible for the development of a purchase-request classification system. Conducted the system analysis, design, and initial implementation, followed by delegation of activities and mentoring of a junior colleague.
        \item \textbf{Cash flow forecast:} Re-engineered preprocessing, training, forecasting, and output pipelines to enhance scalability, reproducibility, and system reliability.
    \end{itemize}}
    \cvitem{\Large{Data Scientist}\hspace{0.5em}\slightlylarger{(2021 - 2024)}}{}
    {\\[-0.5em]\slightlylarger{\emph{Implementation of data-driven solutions based on statistical and ML models.}}
    \addtolength{\leftmargini}{-1.3em}
    \begin{itemize}
        \setlength\itemsep{-0.1em}
        \setlength\topsep{-0.1em}
        \item \textbf{Customer analytics \& demand forecasting:} Contributed to the design of a forecasting system for product mix planning. Performed advanced analyses of user navigation data from e-commerce platforms to support marketing and personalization strategies.
        \item \textbf{Marketing performance measurement:} Developed tools for Marketing Mix Modeling based on open-source libraries. Performed attribution analyses including online and offline channels.
        \item \textbf{NLP \& Deep Learning:} Developed a custom aspect-extraction model in PyTorch and deployed it in a prototype AWS web app for aspect-based sentiment analysis. Experience applying open-source NLP models.
    \end{itemize}}
    \cvitem{\textbf{\Large{\href{https://www.charite.de/en/}{Charitè} / \href{https://www.bccn-berlin.de}{BCCN}}}\hspace{0.5em}\slightlylarger{(2016 - 2021)}\hspace{0.5em}}{\slightlylarger{Berlin}}{}{}
    \cvitem{\Large{Researcher in Cognitive Neuroscience}\hspace{0.5em}\slightlylarger{(2017 - 2021)}}{}
    {\\[-0.5em]\slightlylarger{\emph{Experimental research on brain signals related to decision-making.}}
    \addtolength{\leftmargini}{-1.3em}
    \begin{itemize}
        \setlength\itemsep{-0.1em}
        \setlength\topsep{-0.1em}
        \item \textbf{Experimental design \& data analyses:} Designed and conducted behavioral and neuroimaging experiments on human participants. Developed data analysis pipelines using statistical and ML models.
        \item \textbf{Results dissemination:} Authored peer-reviewed publications, presented research at international conferences. Published anonymized datasets and reproducible code for the research community.
    \end{itemize}}
    \cvitem{\Large{Research Intern}\hspace{0.5em}\slightlylarger{(Feb 2016 - Sep 2016)}}{}
    {\\[-0.5em]\slightlylarger{\emph{Computational neuroscience research conducted for master's thesis abroad.}}
    \addtolength{\leftmargini}{-1.3em}
    \begin{itemize}
        \setlength\itemsep{-0.1em}
        \setlength\topsep{-0.1em}
        \item \textbf{Neuroimaging data analysis:} Experimentation with ML techniques and development of a classification pipeline starting from an existing dataset.
        \item \textbf{Lab work \& programming:} MATLAB programming and collaboration within an interdisciplinary research team.
    \end{itemize}}
\end{cvtable}


\cvsection{\huge{Education}}

\begin{cvtable}[2]
   \cvitem{\textbf{\large{Doctoral Degree}}}{\normalsize{Charitè - Universitätsmedizin Berlin}}{}
   \cvitem{\textbf{\large{Master in Cognitive Neuroscience}}}{\normalsize{Università di Padova}}{}
   \cvitem{\textbf{\large{Bachelor in Psychology}}}{\normalsize{Università di Bologna}}{}
\end{cvtable}

\end{document}